\documentclass[11pt]{article}

\vspace*{-0.5in}
\usepackage[margin=0.6in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{xstring}

\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

\newcommand{\FirstBig}[1]{%
  \StrLeft{#1}{1}[\FirstChar]%
  \StrGobbleLeft{#1}{1}[\RestChars]%
  {\large\bfseries\FirstChar}\RestChars%
}

\titleformat{\section}
  {\scshape\Large}
  {}{0pt}{\FirstBig}[\vspace{2pt}\titlerule]
\titlespacing*{\section}{0pt}{10pt}{6pt}

\setlist[itemize]{leftmargin=1.25em, itemsep=2pt, topsep=2pt}

\newcommand{\twocol}[2]{%
  \begin{tabularx}{\linewidth}{@{}X r@{}}
    \textbf{\FirstBig{#1}} & \textbf{#2} \\
  \end{tabularx}
}

\newcommand{\roleline}[2]{%
  \begin{tabularx}{\linewidth}{@{}X r@{}}
    \textit{#1} & \textit{#2} \\
  \end{tabularx}
}

\begin{document}

% Header
\begin{center}
  {\LARGE\bfseries
    {\huge M}ALAHIM {\huge T}ARIQ
  }\vspace{4pt}\\
  Redmond, WA 98052 \;\textbullet\;
  \href{mailto:mt109@wellesley.edu}{mt109@wellesley.edu} \;\textbullet\;
  929-822-1351 \;\textbullet\;
  \href{https://www.linkedin.com/in/malahim-tariq}{linkedin.com/in/malahim-tariq}
\end{center}

\vspace{2pt}
\noindent\textbf{Product Manager} $|$ \textbf{Platform, Commerce \& Ecosystem Products} \\
\noindent Focused on building \textbf{cross-platform experiences} that scale. Experience owning \textbf{0$\to$1 product delivery}, \textbf{experimentation}, and \textbf{partner integrations} across Xbox gaming commerce (Console, PC, Web, Mobile). Background in \textbf{ML research}, \textbf{data-driven prioritization}, and \textbf{cross-functional execution} spanning engineering, design, legal, and GTM.

% Professional Experience
\section{Professional Experience}

\twocol{Microsoft --- Xbox}{Redmond, WA}
\roleline{Product Manager, Storefront Commerce \& Platform}{Jul 2025 -- Present}
\begin{itemize}
  \item Own third-party subscription integrations and monetization across \textbf{four surfaces} (Console, PC App, Xbox.com, Mobile)---defining product strategy for what users see, how they subscribe, and how entitlements behave across devices.
  \item Led \textbf{0$\to$1} integration of Fortnite Crew and Ubisoft+ Classics into Game Pass Ultimate end-to-end with engineering, design, legal, and finance; expanded access to new subscription catalogs across all client surfaces.
  \item Defined cross-system \textbf{identity and entitlement architecture} (activation, account linking, renewal, revocation, multi-device access), reducing inconsistent user states and purchase ambiguity across the platform.
  \item Designed and evaluated \textbf{product experiments} to improve subscription engagement and conversion; built an \textbf{experimentation skill} into the team's AI system (GitHub Copilot) to standardize hypothesis-driven testing workflows.
  \item Audited the third-party ecosystem and authored \textbf{integration principles} (entitlement standards, UX parity, lifecycle transparency, revenue visibility) that directly shaped \textbf{roadmap prioritization} and partner onboarding.
  \item Built a \textbf{GPT-powered onboarding assistant} for new PMs and interns after observing ramp-up friction; validated with hiring managers and new hires, who cited faster time-to-productivity and clearer role expectations.
  \item Run a recurring \textbf{v-team forum spanning nine organizations}, aligning internal teams, interns, and cross-org partners on priorities, dependencies, and shared outcomes.
\end{itemize}

\twocol{Microsoft --- Xbox}{Redmond, WA}
\roleline{Product Manager Intern --- Xbox Storefront (Commerce)}{May 2024 -- Aug 2024}
\begin{itemize}
  \item Contributed to \textbf{Offer Wallet}, a next-gen promotions platform: improved UX and offer targeting vs.\ legacy tooling; sustained \textbf{$\sim$2$\times$ redemption rates} with a slower post-launch decay curve, indicating stronger user-offer matching.
  \item Defined \textbf{success metrics} and MVP scope; supported a near-doubling of campaign velocity (\textbf{15+} campaigns vs.\ 8 in prior FY), reaching \textbf{500K+} previously untargetable users and projecting \textbf{\$76M} gross revenue vs.\ \$37M prior year.
\end{itemize}

\twocol{Microsoft --- Xbox}{Redmond, WA}
\roleline{Explore Intern (PM + SWE)}{May 2023 -- Aug 2023}
\begin{itemize}
  \item Built storefront features in C\#, TypeScript, and React, developing foundational understanding of large-scale commerce services, entitlement systems, and platform architecture.
\end{itemize}

% Skills
\section{Skills}

\begin{tabularx}{\linewidth}{@{} >{\bfseries}l X @{}}
  Product:       & 0$\to$1 product development, platform \& ecosystem strategy, experimentation \& A/B testing, product analytics (engagement, retention, conversion funnels), roadmap prioritization, stakeholder alignment \\[3pt]
  Technical:     & C\#, Python, SQL, TypeScript, React, Unity (VR), TensorFlow, PyTorch, scikit-learn, Pandas; API design, data modeling, ML foundations \\[3pt]
  Execution:     & Cross-functional leadership (Engineering, Design, GTM, Legal, Finance), partner negotiations, contract-driven delivery, launch readiness orchestration \\[3pt]
  Languages:     & Urdu (fluent), Punjabi (conversational), English (fluent) \\
\end{tabularx}

% Education
\section{Education}

\twocol{Wellesley College}{Wellesley, MA}
\roleline{B.A.\ in Computer Science, Minor in Philosophy}{May 2025}
\vspace{1pt}
\textbf{Coursework:} AI, Algorithms, Statistics, HCI, Data Structures \quad
\textbf{Honors:} Graduation Speaker (First-Gen Ceremony, 2025); Welcome Ceremony Speaker (2023); Camellia Leadership Award Nominee (2024) \\[2pt]
\textbf{ML Research} (Jan--May 2024): Experimented with LSTM and Neural Prophet on NYC taxi data to evaluate ML-driven demand forecasting; supervised by Christine Bassem.

% Leadership
\section{Leadership}
\textbf{Intern culture \& mentorship} -- Interview PM intern candidates; facilitate working sessions with C-suite executives to shape intern programming, cohort culture, and cross-functional collaboration norms. Mentor PM intern through feature scoping and execution. \\
\textbf{MIT GEL} -- Section lead and mentor (TA), Engineering Leadership Lab 6.9110 (Sep 2023 -- May 2025); managed peer mentors, set section vision. \\
\textbf{Digital Literacy Campaign} -- Founded and ran a digital skills program for 200+ girls in Lahore, Pakistan (May 2019 -- Dec 2025); designed curriculum, taught classes.

\end{document}
